Arc Blanc: a real time ocean simulation framework

### 2025-02-05 paper.tex
Made some small typos enhancement

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Water height}
\label{subsec:waterHeight}
Tessendorf (2001) \cite{tessendorfSimulating2001} proposed to solve Equation~\ref{equa:systemTessendorf} using a sum of waves of different amplitudes and wavelengths as follows:
\begin{equation}
	\label{equa:heightWater}
	h(\mathbf x,t)=\sum_{\mathbf{k}} \tilde{h}(\mathbf{k}, t) \exp\left( i \mathbf{k}\cdot \mathbf x\right),
\end{equation}
where $\mathbf{k}=\left[k_x\ k_z\right]^T$ is the wave vector with $k_x=\frac{2\pi n}{L_{i}}$ and $k_z=\frac{2\pi m}{L_{i}}$, $L_i$ is the length of the i-th cascade as defined in Section~\ref{subsec:cascades}, $n$ and $m$ are integers in $\left[-\frac{N}{2},\frac{N}{2}\right]$, $N\in\mathbb N^+$ being a constant given by user, and $\tilde{h}$ is given by:
\begin{equation}
	\label{equa:heightWaterBis}
	\tilde{h}(\mathbf{k}, t) = \tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t),
\end{equation}
where $k$ is the Euclidean norm of the wave vector $\mathbf{k}$, $\omega(k)=\sqrt{gk}$ is the \textbf{dispersion relation}\footnote{The dispersion relation is defined for deep water, see Appendix~\ref{sec:annexe} for more details.} and $\tilde{h}_0^*$ the conjugate of $\tilde{h}_0$.
Researchers in oceanography have made statistical measurements on the ocean to compute $\tilde{h}_0$, leading to many different \textit{ocean spectra} \cite{tessendorfGilliganPrototypeFramework2017}.
In its original paper, Tessendorf (2001) \cite{tessendorfSimulating2001} used the \textit{Phillips Spectrum} with Gaussian fluctuation, leading to the following expression of $\tilde{h}_0(\mathbf{k})$:
\begin{equation}
	\tilde{h}_0(\mathbf{k}) = \xi_{\mathbf{k}}\sqrt{\frac{4\pi}{L_ik}S(\omega)D(\omega, \theta)\left|\frac{\partial\omega(k)}{\partial k}\right|}
\end{equation}
where $\xi_{\mathbf{k}}$ are samples from a Gaussian distribution with mean $0$ and standard deviation $1$, $S(\omega)$ and $D(\omega, \theta)$ are the frequency and directional spectra described respectively in paragraphes \ref{subsubsec:jonswap} and \ref{subsubsec:donelanbanner}.

@@

The pseudo code for the calculations performed in this section can be read in the Algorithm \ref{alg:geom_params}.

@@

Firstly, for each triangle in the mesh, the geometric parameters are calculated and then used to compute the drag forces. These include necessary attributes such as the submerged volume, normal vectors, and the drag forces acting on submerged and non submerged parts.

@@

With all global parameters computed, the final step transfers the data to the CPU, where the physics solver integrates the buoyancy and the water drag forces are applied on the submerged center, while air drag forces are applied at the center of the non submerged part.

@@

\begin{figure}[!h]
	\centering
	\input{Tikz/forcesComputation.tikz}
	\caption{Summary of forces calculation. Using the same notation as Section~\ref{subsec:forces} it follows:
		the buoyancy force \textcolor{jauneC}{$F_b$} in \textcolor{jauneC}{yellow}, applied to the center of immersion;
		the sum of water drag force \textcolor{purpleF}{$F_w$} in \textcolor{purpleF}{purple}, applied to the center of immersion too;
		the sum of the air drag forces \textcolor{redF}{$F_a$} in \textcolor{redF}{red}, applied to the center of the non submerged part;
		and finally the gravity force \textcolor{greenF}{$F_g$} in \textcolor{greenF}{green}, applied to the center of gravity.
		Different velocities are displayed above the ship:
		the wind velocity \textcolor{redF}{$v_a$} in \textcolor{redF}{red};
		the water velocity \textcolor{bleuF}{$v_w$} in \textcolor{bleuF}{blue};
		and the object velocity \textcolor{noirC}{$v$} in \textcolor{noirC}{black}.}
	\label{fig:forcesComputation}
\end{figure}

@@

To ensure high performance, the FDM update step is executed entirely on the GPU,
with a single kernel processing all points of the simulation zone in parallel.
Each thread updates one grid point, significantly reducing computation time. The pseudo code associated to this method is shown in Algorithm \ref{alg:fdm_compute}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained in one of the intersection polygons at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Interface condition}
It is necessary to define a boundary condition at the interface between the ocean fluid and the air fluid.
To simplify, it is assume that the air can be represented as a region with constant pressure\footnote{As shown by the \href{https://en.wikipedia.org/wiki/Barometric_formula}{barometric formula} the atmospheric pressure has a very low evolution in function of altitude.}.
Since air density is a hundred of times lighter than water, its effects on the free surface are assumed to be negligible.
As with an incompressible fluid, only the differences in pressure matter.
Therefore, the air pressure is defined as an arbitrary constant, leading to:
\begin{equation}
	p = 0\text{~~~~~~~~~~~at free surface.}
\end{equation}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Water height}
\label{subsec:waterHeight}
Tessendorf (2001) \cite{tessendorfSimulating2001} proposed to solve Equation~\ref{equa:systemTessendorf} using a sum of waves of different amplitudes and wavelengths as follows:
\begin{equation}
	\label{equa:heightWater}
	h(\mathbf x,t)=\sum_{\mathbf{k}} \tilde{h}(\mathbf{k}, t) \exp\left( i \mathbf{k}\cdot \mathbf x\right),
\end{equation}
where $\mathbf{k}=\left[k_x\ k_z\right]^T$ is the wave vector with $k_x=\frac{2\pi n}{L_{i}}$ and $k_z=\frac{2\pi m}{L_{i}}$, $L_i$ is the length of the $i$-th cascade as defined in Section~\ref{subsec:cascades}, $n$ and $m$ are integers in $\left[-\frac{N}{2},\frac{N}{2}\right]$, $N\in\mathbb N^+$ being a constant given by user, and $\tilde{h}$ is given by:
\begin{equation}
	\label{equa:heightWaterBis}
	\tilde{h}(\mathbf{k}, t) = \tilde{h}_0(\mathbf{k})\exp(i\omega(k)t)+\tilde{h}_0^*(-\mathbf{k})\exp(-i\omega(k)t),
\end{equation}
where $k$ is the Euclidean norm of the wave vector $\mathbf{k}$, $\omega(k)=\sqrt{gk}$ is the \textbf{dispersion relation}\footnote{The dispersion relation is defined for deep water, see Appendix~\ref{sec:annexe} for more details.} and $\tilde{h}_0^*$ the conjugate of $\tilde{h}_0$.
Researchers in oceanography have made statistical measurements on the ocean to compute $\tilde{h}_0$, leading to many different \textit{ocean spectra} \cite{tessendorfGilliganPrototypeFramework2017}.
In its original paper, Tessendorf (2001) \cite{tessendorfSimulating2001} used the \textit{Phillips Spectrum} with Gaussian fluctuation, leading to the following expression of $\tilde{h}_0(\mathbf{k})$:
\begin{equation}
	\tilde{h}_0(\mathbf{k}) = \xi_{\mathbf{k}}\sqrt{\frac{4\pi}{L_ik}S(\omega)D(\omega, \theta)\left|\frac{\partial\omega(k)}{\partial k}\right|}
\end{equation}
where $\xi_{\mathbf{k}}$ are samples from a Gaussian distribution with mean $0$ and standard deviation $1$, $S(\omega)$ and $D(\omega, \theta)$ are the frequency and directional spectra described respectively in paragraphs \ref{subsubsec:jonswap} and \ref{subsubsec:donelanbanner}.

@@

The pseudocode for the all geometrical calculations performed in this section can be read in the Algorithm \ref{alg:geom_params}.

@@

Firstly, for each triangle in the mesh, the geometric parameters are calculated and then used to compute the drag forces. These include necessary attributes such as the submerged volume, normal vectors, and the drag forces acting on submerged and non-submerged parts.

@@

With all global parameters computed, the final step transfers the data to the CPU, where the physics solver integrates the buoyancy and the water drag forces are applied on the submerged center, while air drag forces are applied at the center of the non-submerged part.

@@

\begin{figure}[!h]
	\centering
	\input{Tikz/forcesComputation.tikz}
	\caption{Summary of forces calculation. Using the same notation as Section~\ref{subsec:forces} it follows:
		the buoyancy force \textcolor{jauneC}{$F_b$} in \textcolor{jauneC}{yellow}, applied to the center of immersion;
		the sum of water drag force \textcolor{purpleF}{$F_w$} in \textcolor{purpleF}{purple}, applied to the center of immersion too;
		the sum of the air drag forces \textcolor{redF}{$F_a$} in \textcolor{redF}{red}, applied to the center of the non-submerged part;
		and finally the gravity force \textcolor{greenF}{$F_g$} in \textcolor{greenF}{green}, applied to the center of gravity.
		Different velocities are displayed above the ship:
		the wind velocity \textcolor{redF}{$v_a$} in \textcolor{redF}{red};
		the water velocity \textcolor{bleuF}{$v_w$} in \textcolor{bleuF}{blue};
		and the object velocity \textcolor{noirC}{$v$} in \textcolor{noirC}{black}.}
	\label{fig:forcesComputation}
\end{figure}

@@

To ensure high performance, the FDM update step is executed entirely on the GPU, with a single kernel processing all vertices of the FDM grid in parallel.
Each thread updates one grid point, significantly reducing computation time. The pseudocode associated to this method is shown in Algorithm \ref{alg:fdm_compute}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Calculate the mask}
The FDM needs the height of the vertices below the body.
This is computed from the mask, composed of the vertices of $Z$ contained in one of the intersections polygons at least.
This is done using the \textbf{Point in Polygon} strategy described in Haines (1994) \cite{hainesPointPolygonStrategies1994}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Interface condition}
It is necessary to define a boundary condition at the interface between the ocean fluid and the air fluid.
To simplify, it is assumed that the air can be represented as a region with constant pressure\footnote{As shown by the \href{https://en.wikipedia.org/wiki/Barometric_formula}{barometric formula} the atmospheric pressure has a very low evolution in function of altitude.}.
Since air density is a hundred of times lighter than water, its effects on the free surface are assumed to be negligible.
As with an incompressible fluid, only the differences in pressure matter.
Therefore, the air pressure is defined as an arbitrary constant, leading to:
\begin{equation}
	p = 0\text{~~~~~~~~~~~at free surface.}
\end{equation}
